Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-10 pnas/Towards.tex
Added third column to Fig. 3 with original molecules

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
	\end{subfigure} 
	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
		 \vspace{-20pt} 	
\end{figure}
% -------------- Vertical subfigures: -------------------------------

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
	\end{subfigure} 
	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
		The reconstruction is shown in gray, the (smoothed) ground truth in yellow, and the original molecules are shown in blue to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion. }
		 \vspace{-20pt} 	
\end{figure}
% -------------- Vertical subfigures: -------------------------------
